Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-04-02 paper/manuscript.Rmd
render docx

---
title: Interisland movements and oceanic swimming of woodland caribou in Newfoundland
author: Quinn M.R. Webber^1\*^, Jack G. Hendrix^1^, Alec L. Robitaille^2^,  Eric Vander Wal^1,2^
date: 
    ^1^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial
   University of Newfoundland
    ^2^Department of Biology, Memorial University of Newfoundland, Canada
    #\*Corresponding author: Quinn M.R. Webber (webber.quinn@gmail.com)
output: 
  #  github_document
  # bookdown::pdf_document2:
  #    number_sections: true
  #    toc: false
   bookdown::word_document2:
    reference_docx: template.docx
bibliography: ../references/swim.bib
csl: ecology.csl
---

>>>>

---
title: Interisland movements and oceanic swimming of woodland caribou in Newfoundland
author: Quinn M.R. Webber^1\*^, Jack G. Hendrix^1^, Alec L. Robitaille^2^,  Eric Vander Wal^1,2^
date: 
    ^1^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial
   University of Newfoundland
    ^2^Department of Biology, Memorial University of Newfoundland, Canada
    #\*Corresponding author: Quinn M.R. Webber (webber.quinn@gmail.com)
output: 
   # github_document
   bookdown::word_document2:
    reference_docx: template.docx
bibliography: ../references/swim.bib
csl: ecology.csl
---
